Fourmile

### 2022-10-09 fourmile_dataprocess.Rmd
ok done

ratios_wy <- ratios %>%
  mutate(wy = calcWaterYear(date)) %>%
  group_by(wy) %>%
  summarize_if(is.numeric, sum, na.rm=TRUE) %>%
  slice(-c(11:12)) %>%
  mutate(us1_rr = us1 / prec_12_cmd,
         ds1_rr = ds1 / prec_13_cmd,
         usgs2_rr = usgs2 / prec_10_cmd,
         usgs1_rr = usgs1 / prec_11_cmd)

>>>>

ratios_wy <- ratios %>%
  mutate(wy = calcWaterYear(date)) %>%
  group_by(wy) %>%
  summarize_if(is.numeric, sum, na.rm=TRUE) %>%
  slice(-c(11:12)) %>%
  mutate(us1_rr = ifelse(is.na(us1), 
                          NA, us1 / prec_12_cmd),
         ds1_rr = ifelse(is.na(ds1),
                          NA, ds1 / prec_13_cmd),
         usgs2_rr = ifelse(is.na(usgs2), 
                            NA, usgs2 / prec_10_cmd),
         usgs1_rr = ifelse(is.na(usgs1),
                            NA, usgs1 / prec_11_cmd))
